---
title: "Linked emulation"
output: rmarkdown::html_vignette
description: >
  Linked (D)GP emulation of a synthetic system of two linked computer models.
vignette: >
  %\VignetteIndexEntry{linked_DGP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE
)
```

## Load the package

```{r}
library(dgpsi)
init_py()
```

## Construct two synthetic models and their linked model

```{r}
#Model 1
f1 <- function(x) {
  (sin(7.5*x)+1)/2
}
#Model 2
f2 <- function(x) {
  2/3*sin(2*(2*x-1))+4/3*exp(-30*(2*(2*x-1))^2)-1/3  
}
#Linked model 
f12 <- function(x) {
  f2(f1(x))
}
```

## Set up training datasets for both models

```{r}
X1 <- as.matrix(seq(0, 1, length = 9))
X2 <- as.matrix(seq(0, 1, length = 13))
Y1 <- as.matrix(sapply(X1, f1))
Y2 <- as.matrix(sapply(X2, f2))
```

## Set up testing datasets

```{r}
test_x1 <- as.matrix(seq(0, 1, length = 300))
test_x2 <- as.matrix(seq(0, 1, length = 300))
test_y1 <- as.matrix(sapply(test_x1, f1))
test_y2 <- as.matrix(sapply(test_x2, f2))
test_y <- as.matrix(sapply(test_x1, f12))
```

## Emulation of the first model

### Construct a GP for the first model

```{r}
m1 <- gp(X1, Y1, kernel(length = c(1.0), name = 'matern2.5', scale_est = TRUE))
m1_trained <- train(m1)
```

### Evaluate the GP emulator for model 1 over [0,1]

```{r}
res1 <- predict(m1_trained, x = test_x1)

mu1 <- res1$mean
sd1 <- sqrt(res1$var)
up1 <- mu1 + 2*sd1
lo1 <- mu1 - 2*sd1

plot(test_x1, mu1, type='l',col='blue',xlab='x1', cex.axis=1.3,cex.lab=1.3, ylab='y1',ylim=c(-0.2,1.2))
polygon(c(test_x1,rev(test_x1)),c(up1,rev(lo1)),col='grey80',border=F)
lines(test_x1,mu1,type='l',col='blue')
lines(test_x1,test_y1,type='l',col='red')
lines(X1,Y1,type='p',cex=0.8)
```

### Create a container for the first emulator

```{r}
c1 <- container(export(m1), c(1))
```

## Emulation of the second model

### Construct a DGP for the second model

```{r}
layer1 <- c(kernel(length = c(1.), name = 'matern2.5'))
layer2 <- c(kernel(length = c(1.), name = 'matern2.5', scale_est = TRUE))
all_layer <- combine(layer1, layer2)
m2 <- dgp(X2, Y2, all_layer)
m2_trained <- train(m2)
```

### Evaluate the DGP emulator for model 2 over [0,1]

```{r}
#Construct emulator
trained_struc <- estimate(m2_trained)
emu <- emulator(trained_struc)
```

```{r}
#Make predictions
res2 <- predict(emu, x = test_x2)

mu2 <- res2$mean
sd2 <- sqrt(res2$var)
up2 <- mu2 + 2*sd2
lo2 <- mu2 - 2*sd2

plot(test_x2, mu2, type='l',col='blue',xlab='x2', cex.axis=1.3,cex.lab=1.3, ylab='y2',ylim=c(-1.2,1.7))
polygon(c(test_x2,rev(test_x2)),c(up2,rev(lo2)),col='grey80',border=F)
lines(test_x2,mu2,type='l',col='blue')
lines(test_x2,test_y2,type='l',col='red')
lines(X2,Y2,type='p',cex=0.8)
```

### Create a container for the second emulator

```{r}
c2 <- container(trained_struc, c(1))
```

## Linking two emulators

### Construct linked emulator

```{r}
struc <- combine(c(c1), c(c2))
lm <- lgp(struc)
```

### Make predictions from the linked emulator

```{r}
res <- predict(lm, x = test_x1)

mu <- res$mean$emulator1
sd <- sqrt(res$var$emulator1)
up <- mu + 2*sd
lo <- mu - 2*sd

plot(test_x1, mu, type='l',col='blue',xlab='x1', cex.axis=1.3,cex.lab=1.3, ylab='y1',ylim=c(-1.2,1.7))
polygon(c(test_x1,rev(test_x1)),c(up,rev(lo)),col='grey80',border=F)
lines(test_x1,mu,type='l',col='blue')
lines(test_x1,test_y,type='l',col='red')
```
